Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-02 SWoPP2018 Paper/paper.tex
Small changes.

\section{Methodology}\label{sec:method}
\subsection{Experimental Platform}
The software versions and hardware configuration are shown in respectively \cref{tab:software-versions} and \cref{tab:test-hardware}.
All kernels were compiled with \texttt{-O3 -fp-relaxed}.
\texttt{-fp-relaxed} gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit without changing the numerical output.
\begin{table}[h]
  \centering
  \caption{Used software versions}\label{tab:software-versions}
  \begin{tabular}{ll}
    \toprule
    \textbf{Software} & \textbf{Version} \\
    \midrule
    Python & v3.6.3 \\
    Keras & v2.2.0 \\
    TensorFlow & v1.8.0 \\
    Intel Quartus & v17.1.0 \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[h]
  \centering
  \caption{Test hardware}\label{tab:test-hardware}
  \begin{tabular}{ll}
    \toprule
    \textbf{Hardware} & \textbf{Configuration} \\
    \midrule
    Intel i7-3930K & \SI{3.20}{\giga\hertz} \\
    Host RAM & DDR3-\SI{1333}{\mega\hertz} Dual Channel \\
    Arria 10 ($\times$1) & Nallatech 510T \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Network Tested + Data-set}
The used example network is a simple multilayer perceptron.
The first dataset used was MNIST, so \num{784} input features.
The structure of the sample MNIST network is.
\begin{enumerate}
  \item Dense(512)
  \item Relu
  \item Dense(512)  
  \item Relu
  \item Dense(10)
  \item Softmax
\end{enumerate}
So in total a three layer network, or threes sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST dataset.
The last \num{10000} images are used as the test data set.
The second dataset used was CIFAR10, so \num{3072} input features.
The structure of the sample CIFAR10 network is.
\begin{enumerate}
  \item Dense(1024)
  \item Relu
  \item Dense(512)  
  \item Relu
  \item Dense(512)  
  \item Relu
  \item Dense(10)
  \item Softmax
\end{enumerate}

The data set was trained using the first \num{50000} images form the dataset.
The last \num{10000} images were used as the test data set.
All training was done using a batch size of \num{128}.
The CPU code was implemented using the NumPy array.dot function.

>>>>

\section{Methodology}\label{sec:method}
\subsection{Experimental Platform}
The software versions and hardware configuration are shown in respectively \cref{tab:software-versions} and \cref{tab:test-hardware}.
All kernels were compiled with \texttt{-O3 -fp-relaxed}.
\texttt{-fp-relaxed} gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit without changing the numerical output.
\begin{table}[h]
  \centering
  \caption{Used software versions}\label{tab:software-versions}
  \begin{tabular}{ll}
    \toprule
    \textbf{Software} & \textbf{Version} \\
    \midrule
    Python & v3.6.3 \\
    Keras & v2.2.0 \\
    TensorFlow & v1.8.0 \\
    Intel Quartus & v17.1.0 \\
    \bottomrule
  \end{tabular}
\end{table}
\begin{table}[h]
  \centering
  \caption{Test hardware}\label{tab:test-hardware}
  \begin{tabular}{ll}
    \toprule
    \textbf{Hardware} & \textbf{Configuration} \\
    \midrule
    Intel i7-3930K & \SI{3.20}{\giga\hertz} \\
    DDR3 RAM & \SI{1333}{\mega\hertz} Dual Channel \\
    Arria 10 ($\times$1) & Nallatech 510T \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Network Tested + Data-set}
The used example network is a simple multilayer perceptron.
The first dataset used was MNIST, so \num{784} input features.
The structure of the sample MNIST network is.
\begin{enumerate}
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}
So in total a three layer network, or threes sets of weight matrices and bias vectors.
The data set was trained using the first \num{60000} images from the MNIST dataset.
The last \num{10000} images are used as the test data set.
The second dataset used was CIFAR10, so \num{3072} input features.
The structure of the sample CIFAR10 network is.
\begin{enumerate}
  \item Dense(1024)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(512)  \(\to\)  Relu
  \item Dense(10)  \(\to\)  Softmax
\end{enumerate}

The data set was trained using the first \num{50000} images from the dataset.
The last \num{10000} images were used as the test data set.
All training was done using a batch size of \num{128}.
The CPU code was implemented using the NumPy array.dot function.
